SVIVA_experiment 2

### 2018-05-18 SVIVA_exp2_01.Rmd
12.3.18_01
Add files via upload

---
title: "SVIVA_experiment 2"
author: "Saar Alon-Barkat"
date: "January 2018"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
---

@@

```{r , include=FALSE, echo=FALSE}
load(".RData")
```

@@

```{r}
t = SVIVA2_00 %>%
  filter(TRUST_air_timer>=10|
           TRUST_waste_timer>=10)
```
*	Answering the two sets of DV questions (trust in air pollution and waste policies) in less than 10 seconds each: `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r}
t = SVIVA2_00 %>%
  filter(REPETITION_elaboration==0)
```

*	Repetition of the same value (except 4) in the elaboration questions (which include 2 reversed items, on a scale of 1 to 7): `r N-nrow(t)` observations (`r round((N-nrow(t))/N*100,1)`%)

```{r,warning=FALSE,message=FALSE}
SVIVA2_01 = SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE) %>% #exclude double IP
  filter(!(AGE %in% 1:17),
         IMC==1,
         TIMER_total>=3,TIMER_total<=30,  
         TRUST_air_timer>=10|
           TRUST_waste_timer>=10, 
         REPETITION_elaboration==0)
```

@@

```{r,warning=FALSE,message=FALSE}
SVIVA2_00 = SVIVA2_00 %>%
  mutate(FILTER_TOTAL = if_else(!(AGE %in% 1:17)&
                                 IMC==1&
                                 TIMER_total>=3 & TIMER_total<=30 &  
                                 (TRUST_air_timer>=10|
                                   TRUST_waste_timer>=10)& 
                                 REPETITION_elaboration==0,0,1))

@@

@@

The first plot shows the distribution of the reaction time (RT) measured in seconds. To reduce skewness, I log transformed this measure, according to the following formula: 
$ELABORATION timelog = log(ELABORATIONtime+1)$

@@

#Policies Combined
```{r}
xx0 = SVIVA2_01 %>% select(IP,AREA,AREA_names,
                      RELEVANCE_exp,RELEVANCE_exp_n,
                      SYMBOL,SYMBOL_n,
                      INFORMATION_air,INFORMATION_air_n,
                      INFORMATION_waste,INFORMATION_waste_n,
                      TRUST_air_INDEX,
                      TRUST_waste_INDEX,
                      ELABORATION_air_time_log,
                      ELABORATION_waste_time_log,
                      GOV_TRUST) %>% 
 gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
                              INFORMATION_waste),
         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
                              INFORMATION_waste_n),
         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
                              ELABORATION_waste_time_log))

>>>>

---
title: "SVIVA_experiment 2"
author: "Saar Alon-Barkat"
date: "January 2018"
output:
  html_document:
    code_folding: hide
    always_allow_html: yes
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
---

@@

```{r , include=FALSE, echo=FALSE}
load("SVIVA_R_ENV.RData")
```

@@

```{r,warning=FALSE,message=FALSE}
SVIVA2_01 = SVIVA2_00 %>%
  distinct(IP,.keep_all=TRUE) %>% #exclude double IP
  filter(!(AGE %in% 1:17),
         IMC==1,
         TIMER_total>=3,TIMER_total<=30)#,  
         #TRUST_air_timer>=10|
          # TRUST_waste_timer>=10, 
         #REPETITION_elaboration==0)
```

@@

```{r,warning=FALSE,message=FALSE}
SVIVA2_00 = SVIVA2_00 %>%
  mutate(FILTER_TOTAL = if_else(!(AGE %in% 1:17)&
                                 IMC==1&
                                 TIMER_total>=3 & TIMER_total<=30,0,1))

@@

sjt.grpmean(SVIVA2_01[,c("INCOME")],factor(SVIVA2_01$AREA))

@@

The first plot shows the distribution of the reaction time (RT) measured in seconds. To reduce skewness, I log transformed this measure, according to the following formula:

@@

#Policies Combined
```{r}
xx0 = SVIVA2_01 %>% dplyr::select(IP,AREA,AREA_names,
                      RELEVANCE_exp,RELEVANCE_exp_n,
                      SYMBOL,SYMBOL_n,
                      INFORMATION_air,INFORMATION_air_n,
                      INFORMATION_waste,INFORMATION_waste_n,
                      TRUST_air_INDEX,
                      TRUST_waste_INDEX,
                      ELABORATION_air_time_log,
                      ELABORATION_waste_time_log,
                      GOV_TRUST) %>% 
 gather(key=policy,value=trust,TRUST_air_INDEX,TRUST_waste_INDEX) %>% 
  mutate(INFORMATION = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air,
                              INFORMATION_waste),
         INFORMATION_n = ifelse(policy=="TRUST_air_INDEX",INFORMATION_air_n,
                              INFORMATION_waste_n),
         ELABORATION_time_log = ifelse(policy=="TRUST_air_INDEX",ELABORATION_air_time_log,
                              ELABORATION_waste_time_log))
